---
title: "Final Project Data Analysis"
author: "Ruiming"
output: 
  pdf_document:
    keep_tex: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Library

```{r}
library(glmnet)
library(e1071)
library(umap)
library(randomForest)
library(MASS)
```

## Data Load

```{r}
if (!require('this.path')) install.packages('this.path')
library(devtools)
library(this.path)
cur_dir2 = dirname(this.path())
cur_dir2
load(paste(cur_dir2, "/MyData.RData", sep = ""))
my_data <- MyDataSet
users <- users
train <- MyTrain
test <- MyTest
train_pca <- MyTrain_pca
test_pca <- MyTest_pca
train_rf <- MyTrain_RF
test_rf <- MyTest_RF
```

```{r}
if (!require('this.path')) install.packages('this.path')
library(devtools)
library(this.path)
cur_dir2 = dirname(this.path())
cur_dir2
load(paste(cur_dir2, "/first_urser_data.RData", sep = ""))
train <- MyTrain
test <- MyTest
my_data <- MyDataSet
users <- users
train_pca <- MyTrain_pca
test_pca <- MyTest_pca
train_rf <- MyTrain_rf
test_rf <- MyTest_rf
```
```

## Data Spliting

```{r}
set.seed(432)
train_index <- sample(1:nrow(my_data), 0.8*nrow(my_data))
train <- as.matrix(my_data[train_index,2:ncol(my_data)])
test <-  as.matrix(my_data[-train_index,2:ncol(my_data)])

# make data into numeric
train <- matrix(as.numeric(apply(train, c(1, 2), as.numeric)), nrow = nrow(train), ncol = ncol(train))
colnames(train) <- colnames(my_data)[2:ncol(my_data)]
test <- matrix(as.numeric(apply(test, c(1, 2), as.numeric)), nrow = nrow(test), ncol = ncol(test))
colnames(test) <- colnames(my_data)[2:ncol(my_data)]
```

## Data Preprocessing


```{r}
#PCA
pca <- prcomp(train[,-1], center = TRUE, scale. = TRUE)
# plot the variables importance
plot(pca, type = "l")
```

```{r}
```

```{r}
# lm 
lm_model <- lm(train[,1] ~0+ ., data = data.frame(train[,-1]))
summary(lm_model)
```

```{r}
# lasso

lasso_model <- cv.glmnet(train[,-1], train[,1], alpha = 1, family = "binomial", nfolds = 15)
plot(lasso_model)
coef(lasso_model, s = "lambda.min")
coef(lasso_model, s = "lambda.1se")
summary(lasso_model)
```

```{r}
# UMAP
umap_result <- umap(train[,-1], n_neighbors = 10, n_components = 4, metric = "euclidean")
plot(umap_result$layout, col = train[,1])
```

```{r}
# ramdom forest

rf_model <- randomForest(as.factor(train[,1]) ~ ., data = data.frame(train[,-1]))
rf_model

# predict error
pred <- predict(rf_model, newdata = data.frame(test[,-1]))
mean((pred - test[,1])^2)

#confusion matrix
table(pred, test[,1])
```

```{r}
# LDA for 12 classes
lda_model <- lda(train[,1] ~ ., data = data.frame(train[,-1]))
lda_model
# confusion matrix
pred <- predict(lda_model, newdata = data.frame(test[,-1]))
table(pred$class, test[,1])
```


```{r}
# UMAP for the first 3 PCA
umap_result <- umap(train_pca[,1:2], n_neighbors = 15, n_components = 2, metric = "euclidean")
plot(umap_result$layout, col = train[,1])
x <- predict(umap_result, test_pca[,1:2])

# use kmeans to do the clustering based on the umap result
kmeans_result <- kmeans(umap_result$layout, centers = 12)
plot(umap_result$layout, col = kmeans_result$cluster)

# confusion matrix
table(kmeans_result$cluster, train[,1])
```


## Crossing Variables
```{r}
# crossing variable 
cross_terms_rowwise <- function(row) {
  combn(row, 2, FUN = function(x) x[1] * x[2])
}

# 应用这个函数到每一行
crossing <- t(apply(train[,-1], 1, cross_terms_rowwise))



# PCA
pca <- prcomp(crossing, center = TRUE, scale. = TRUE)
# plot the variables importance
plot(pca, type = "l")
```

```{r}
# lm
lm_model <- lm(train[,1] ~0+ ., data = data.frame(crossing))
summary(lm_model)
```

```{r}
# umap
n = 3
umap_result <- umap(pca$x[,1:3], n_neighbors = 15, n_components = 2, metric = "euclidean")
plot(umap_result$layout, col = train[,1])

# use kmeans to do the clustering based on the umap result
kmeans_result <- kmeans(umap_result$layout, centers = 12)
plot(umap_result$layout, col = kmeans_result$cluster)

# confusion matrix
table(kmeans_result$cluster, train[,1])
```

```{r}
```

```{r}
# plot the first two PCA
plot(pca$x[,2:3], col = train[,1])


```

```{r}
# plot the first two important variables based on random forest
varImpPlot(rf_model)

# use the first two important variables to do the umap
umap_result <- umap(train[,c(18,12)], n_neighbors = 5, n_components = 4, metric = "euclidean")
plot(umap_result$layout, col = train[,1])

# use kmeans to do the clustering based on the umap result
kmeans_result <- kmeans(umap_result$layout, centers = 12)
plot(umap_result$layout, col = kmeans_result$cluster)

# confusion matrix
table(kmeans_result$cluster, train[,1])
```

```{r}
```

```{r}


```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```





